\chapter*{\hfill Publications}
\addcontentsline{toc}{chapter}{Publications} 


The following publications have resulted from the research contained in this Thesis:

\vspace{0.5in}
\begin{minipage}{\linewidth}
M. Thornton, H. Scott, C. Croal and N. Korolkova: \\
\emph{Continuous-variable quantum digital signatures over insecure quantum channels}, \\
Physical Review A \textbf{99}, $032341$, $\left(2019\right)$.
\end{minipage}

\vspace{0.25in}
\begin{minipage}{\linewidth}
M. Thornton, A. Sakovich, A. Mikhalychev, J. D. Ferrer, P. de la Hoz, N. Korolkova and D. Mogilevtsev: \\
\emph{Coherent diffusive photon gun for generating nonclassical states}, \\
Physical Review Applied \textbf{12}, $064051$, $\left(2019\right)$.
\end{minipage}

\vspace{0.25in}
\begin{minipage}{\linewidth}
S. Richter, M. Thornton, I. Khan, H. Scott, K. Jaksch, U. Vogl, B. Stiller, G. Leuchs, C. Marquardt and N. Korolkova: \\
\emph{Agile quantum communication: signatures and secrets}, \\
arXiv:$2001.10089$ [quant-ph].
\end{minipage}

%\vspace{0.5in}
%{\let\cleardoublepage\relax \chapter*{\hfill Conference Presentations}}


\chapter*{\hfill Conference Presentations}
\addcontentsline{toc}{chapter}{Conference Presentations} 
I have had the privilege to present at the following conferences:

\begin{enumerate}
\item QCrypt $2016$, Washington DC, USA. Poster presentation: ``Continuous variable quantum digital signatures.''
%\item CEWQO $2017$, Copenhagen, Denmark. Poster presentation: ``Gigahertz quantum signatures compatible with telecommunication technologies.''
\item $6^{\text{th}}$ International Conference on New Frontiers in Physics (ICNFP $2017$), Kolymbari, Crete. Oral presentation: ``Gigahertz quantum signatures compatible with telecommunication technologies.''
\item QCrypt $2017$, Cambridge, UK. Poster presentation: ``Gigahertz quantum signatures compatible with telecommunication technologies.''
\item WE-Heraeus-Seminar on ``Quantum Correlations in Space and Time,'' $2017$, Bad Honnef, Germany. Poster presentation: ``Gigahertz quantum signatures compatible with telecommunication technologies.''
\item $25^{\text{th}}$ Central European Workshop on Quantum Optics (CEWQO $2018$), Palma de Mallorca, Spain. Poster presentation: ``Gigahertz quantum signatures compatible with telecommunication technologies.''
\item $24^{\text{th}}$ Young Atom Opticians (YAO $2018$), Glasgow, Scotland. Poster presentation: ``Coherent quantum networks for non-classical state generation.''
\item Quantum Roundabout $2018$, Nottingham, UK. Poster presentation: ``Efficient generation of sub-Poissonian light via coherent diffusive photonics.''
\item $1^{\text{st}}$ European Quantum Technologies Conference (EQTC $2019$), Grenoble, France. Poster presentation: ``Efficient generation of sub-Poissonian light via coherent diffusive photonics.''
\item ICQOQI $2019$, Minsk, Belarus. Oral presentation: ``Continuous-variable quantum digital signatures over insecure channels.''
\item Quantum Information Scotland (QUISCO) September $2019$, St Andrews, Scotland. Oral presentation: ``Agile quantum communication: quantum signatures and quantum secrets.''
\end{enumerate}




