\chapter*{\hfill Collaboration statement}
\addcontentsline{toc}{chapter}{Collaboration Statement} 

This Thesis is the result of work which I carried out at the University of St Andrews between September $2016$ and March $2020$. Much of the work contained here has been published in (or submitted to) refereed scientific journals. All text in this Thesis has been written entirely by me. Unless otherwise stated, all figures have been created entirely by me.

Content in Chapter~\ref{chapter:qds} and Appendix~\ref{appendix:qds_larger_alphabets} is also contained in M. Thornton \emph{et. al.}, Phys. Rev. A \textbf{99}, $032341$ ($2019$). Theoretical work was conducted in collaboration with H. Scott. All numerics used to generate results and figures in Ch.~\ref{chapter:qds} were created by me. 

Chapters~\ref{chapter:qss} and \ref{chapter:aqc} are extensions of work contained in S. Richter \emph{et. al.}, arXiv:$2001.10089$ [quant-ph]. The original ideas and framework underpinning Ch.~\ref{chapter:aqc} were formulated during discussions I partook in at the Max-Planck-Institute f{\"u}r die Physik des Lichts (MPL) in Erlangen, Germany in May $2017$. The work was completed in collaboration with S. Richter, I. Khan and C. Marquardt. My contribution was the theoretical analysis and security proofs which underpin the chapters, while the experiment discussed in Sec.~\ref{sec:aqc_experiment} was performed at MPL by S. Richter and I. Khan, with assistance from K. Jaksch, U. Vogl, B. Stiller, G. Leuchs and C. Marquardt. I analysed experimental data with additional assistance from S. Richter and I. Khan. 

Chapter~\ref{chapter:phog} is an expansion on content contained in M. Thornton \emph{et. al.}, Phys. Rev. Applied \textbf{12}, $064051$, ($2019$). N. Korolkova and D. Mogilevtsev provided the direction and original ideas for the work. The work contained in Ch.~\ref{chapter:phog} was carried out by myself in collaboration with D. Mogilevtsev and P. de la Hoz, and with assistance from A. Sakovich for the numerics. 

All work in this Thesis has been supported by my supervisor, Professor N. Korolkova.